---
title: "Final_Report_Xinyu_Zhang"
author: "Xinyu Zhang"
date: "`r Sys.Date()`"
output: html_document
---

```{r,set-up-chuncks,echo=FALSE,eval=FALSE}
library(knitr)
opts_chunk$set(
  echo=FALSE, warning= FALSE, message = FALSE
)
```


# Dataset introduction

The [dataset](https://www.kaggle.com/datasets/rabieelkharoua/alzheimers-disease-dataset) we are going to use is shared by [Rabie El Kharoua](https://www.kaggle.com/rabieelkharoua) and downloaded from Kaggle.
It is a dataset with 35 variables and 2149 observations.
The data was pre-cleaned and the variables can be categorized into several categories: 

- Demographic Details(Age, Gender, Ethnicity, Educationlevel).

- Lifestyle Factors (BMI, Smoking, AlcoholConsumption,PhysicalActivity,DietQuality,SleepQuality).

- Medical History (FamilyHistoryAlzheimers,CardiovascularDisease,Diabetes,Depression,HeadInjury,Hypertension).

- Clinical Measurements(SystolicBP,DiastolicBP,CholesterolTotal,CholesterolLDL,CholesterolHDL,CholesterolTriglycerides).

- Cognitive and Functional Assessments(MMSE,FunctionalAssessment,MemoryComplaints,BehavioralProblems,ADL).

- Symptoms(Confusion,Disorientation,PersonalityChanges,DifficultyCompletingTasks,Forgetfulness).

as well as their own patient ID and Alzheimer's diagnostic informations, we drop DoctorInCharge off from the start because it is the same for all patients and could not provide any information.


```{r}
here::i_am("Final_Report_Xinyu_Zhang.Rmd")
az_data<-readRDS(
  file = here::here("02_Output/az_data_clean.rds")
)
```

# Tabular Summary:

```{r,table1}
table_one <-readRDS(
  file = here::here("02_Output/table_one.rds")
)
table_one
```

# Graphs

```{r,plot_data_1}
#| fig.glign="center",
#| out.width="600px"
knitr::include_graphics(
  here::here("03_Figure/boxplot_M_d.png")
)
 
```

```{r,plot_data_2}
#| fig.glign="center",
#| out.width="600px"
knitr::include_graphics(
  here::here("03_Figure/boxplot_M_E.png")
)

```

# Regression output

```{r, table1_1}
regression_output <- readRDS(
  file = here::here("02_Output/logit_model.rds")
)
regression_output
```

## AUC curve:

```{r,plot_data_3}
#| fig.glign="center",
#| out.width="600px"
knitr::include_graphics(
  here::here("03_Figure/AUC_curve.png")
)

```
